---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Status and Trends of Coral Reefs of the Pacific**


## 1. Introduction

## 2. Code

### A. Cleaning and selection (`01_`)

* `01_benthic_data_sources.R` Extract data sources from [gcrmndb_benthos](https://github.com/JWicquart/gcrmndb_benthos).
* `01_clean_bathy.R` Clean bathymetry data from [Natural Earth Data](https://www.naturalearthdata.com/downloads/10m-physical-vectors/).
* `01_clean_cyclones.R` Clean cyclone dataset from [IBTrACS](https://www.ncei.noaa.gov/products/international-best-track-archive).
* `01_clean_eez.R` Select and clean economic exclusive zones (EEZ) from [marineregions](https://marineregions.org/downloads.php).
* `01_clean_land.R` Clean Pacific land data (high spatial resolution) from [Princeton University](https://maps.princeton.edu/).
* `01_clean-reef-distribution.R` Select Pacific coral reefs distribution from the [Tropical Coral Reefs of the World](https://datasets.wri.org/dataset/tropical-coral-reefs-of-the-world-500-m-resolution-grid) World Resources Institute (WRI).
* `01_download_coraltemp.R` Download [CoralTemp](https://coralreefwatch.noaa.gov/index.php) NetCDF4+ files for SST and DHW.
* `01_select_benthic-data.R` Select [gcrmndb_benthos](https://github.com/JWicquart/gcrmndb_benthos) data to use in the analyses.

### B. Extraction and models (`02_`)

#### B1. Indicators

* `02_extract_indicator_cyclones` Extract cyclones for each EEZ.
* `02_extract_dhw-percent.R` Extract percent of coral reefs under DHW for each EEZ.
* `02_extract_dhw-time-series.R` Extract maximum DHW within each EEZ.
* `02_extract_elevation.js` Extract mean land elevation for each territory using Google Earth Engine (GEE). Estimated values are used as geographic information's.
* `02_extract_land-area.js` Extract total land area for each territory using GEE. Estimated values are used as geographic information's.
* `02_extract_map-dhw.R` Create raster with the mean annual DHW for each cell.
* `02_extract_population.R` Extract human population for each territory. Estimated values are used as geographic information's.
* `02_reef-buffer.js` Create coral reef distribution buffer of 100 km. Used to extract cyclones occurrence.
* `02_extract_sst-time-series.R` Extract SST and SST anomaly on coral reefs of each EEZ.

#### B2. Predictors

* `02_extract_predictor_population.js` Extract total human population within 10 km from each site as a predictor, using GEE.
* `02_extract_predictor_elevation.js` Extract mean land elevation within 10 km from each site as a predictor, using GEE.
* `02_extract_predictor_reef-extent.js` Extract total coral reef extent within 10 km from each site as a predictor, using GEE.
* `02_extract_predictor_land.js` Extract total land area within 10 km from each site as a predictor, using GEE.

#### B3. Models

* `02_model_data-exploration.Rmd` Data exploration for benthic cover.
* `02_model_benthic-data_grid.R` Create weights for the benthic model based on coral reef extent.
* `02_model_benthic-cover.R` Machine learning model to estimate temporal trends of hard coral and algae cover. 

### C. Figures and tables (`03_`)

* `03_benthic-cover-trends.Rmd` Produce figures of hard coral and algae cover trends.
* `03_geographic-informations.R` Combine and export geographic information's.
* `03_materials-and-methods.R` Produce figures for the Materials and Methods section of the report.
* `03_pacific_cyclones.R` Produce figure and map of cyclones that occurred over the Pacific region.
* `03_pacific_enso.R` Produce figure of ENSO.
* `03_pacific_map.R` Produce map of the entire Pacific GCRMN region with description of EEZ.
* `03_pacific_map-dhw.R` Produce map of DHW for each year.
* `03_pacific_population.R` Produce figure of human population change between 2000 and 2020.
* `03_pacific_rel-reef-area.R` Produce figure of relative reef area of Pacific territories.
* `03_pacific_spatio-temporal.R` Produce figure and map of spatio-temporal distribution of benthic cover monitoring for the Pacific region.
* `03_pacific_sst.R` Produce figures of maximum DHW and DHW percent for the Pacific region.
* `03_territories_cyclones.R` Produce figures and maps of cyclones that occurred on each EEZ.
* `03_territories_map-bathy.R` Produce EEZ maps.
* `03_territories_map-sphere.R` Produce hemisphere maps for each EEZ.
* `03_territories_spatio-temporal.R` Produce figure and map of spatio-temporal distribution of benthic cover monitoring for each EEZ.
* `03_territories_sst.R` Produce figures of SST, SST anomaly and DHW for each EEZ.

### D. Functions

* `data_descriptors.R` Get number of sites, surveys, datasets, first and last year of monitoring.
* `graphical_par.R` Graphical parameters, including colors and fonts.
* `taxonomic_levels.R` Produce plot of percentage of rows per taxonomic level.
* `theme_graph.R` Main ggplot theme for the maps of the reports.
* `theme_map.R` Main ggplot theme for the plots of the reports.


## 3. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Print session info ----

devtools::session_info(c("sf", "terra", "tidyverse", "tidymodels"))

```
