---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Status and Trends of Coral Reefs of the Pacific**


## 1. Introduction

## 2. Code

### Functions

* `data_descriptors.R` Get number of sites, surveys, datasets, first and last year of monitoring.
* `graphical_par.R` Graphical parameters, including colors and fonts.
* `theme_graph.R` Main ggplot theme for the plots of the reports.
* `theme_map.R` Main ggplot theme for the maps of the reports.

### Cleaning and selection (`a_`)

* `a1_select_benthic-data.R` Select [gcrmndb_benthos](https://github.com/JWicquart/gcrmndb_benthos) data to use in the analyses.
* `a2_benthic_data_sources.R` Extract data sources from [gcrmndb_benthos](https://github.com/JWicquart/gcrmndb_benthos).
* `a3_clean_eez.R` Select and clean economic exclusive zones (EEZ) from [marineregions](https://marineregions.org/downloads.php).
* `a4_clean_land.R` Clean Pacific land data (high spatial resolution) from [Princeton University](https://maps.princeton.edu/).
* `a5_clean_bathy.R` Clean bathymetry data from [Natural Earth Data](https://www.naturalearthdata.com/downloads/10m-physical-vectors/).
* `a6_clean-reef-distribution.R` Select Pacific coral reefs distribution from the [Tropical Coral Reefs of the World](https://datasets.wri.org/dataset/tropical-coral-reefs-of-the-world-500-m-resolution-grid) World Resources Institute (WRI).
* `a7_reef-buffer.js` Create 100 km reef buffer using Google Earth Engine (GEE). 
* `a8_clean_cyclones.R` Clean cyclone dataset from [IBTrACS](https://www.ncei.noaa.gov/products/international-best-track-archive).
* `a9_extract_dhw-year.R` Create TIFF files of maximum DHW per year using [Coral Reef Watch data](https://coralreefwatch.noaa.gov/product/5km/index_5km_dhw.php).

### Extract indicators (except benthic cover) (`b_`)

* `b1_extract_indicator_land.js` Extract total land area for each EEZ using GEE.
* `b2_extract_indicator_elevation.js` Extract mean land elevation for each EEZ using GEE.
* `b3_extract_indicator_population.js` Extract human population for each EEZ using GEE. 
* `b4_extract_indicator_sst.R` Extract SST on coral reefs for each EEZ.
* `b5_extract_indicator_cyclones.R` Extract cyclones on coral reefs for each EEZ.

### Models (benthic cover) (`c_`)

* `c1_select_pred-sites.js`
* `c2_extract_predictor_gee.js`
* `c3_extract_predictor_gravity.R`
* `c4_extract_predictor_enso.R`
* `c5_extract_predictor_cyclones.R`
* `c6_extract_predictor_dhw-year.R`
* `c7_model_data-preparation.R` 
* `c8_model_data-exploration.R`

### Figures and tables (`d_`)

* `d1_materials-and-methods.R`
* `d2_pacific_map.R`        
* `d3_territories_map.R`
* `d4_pacific_sst.R`
* `d5_territories_sst.R`              
* `d6_pacific_cyclones.R`
* `d7_territories_cyclones.R`
* `d8_pacific_spatio-temporal.R`      
* `d9_territories_spatio-temporal.R`
* `d10_benthic-cover_trends.R`  
* `d11_other-indicators.R`
* `d12_case-studies.R`

## 3. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Print session info ----

devtools::session_info(c("sf", "terra", "tidyverse", "tidymodels"))

```
